Are rankings of financial analysts useful to investors?

### 2015-03-17 doc/paper/paper-knitr-APS.Rnw
modify rnw for different types of stock sets

stat.nr <- rbind(na.omit(nr.views)[,list(mean=mean(View),median=median(View),st.dev=sd(View),Stocks=length(unique(Stock))),by=.(year,Method)],setnames(cbind('Total',na.omit(nr.views)[,list(mean=mean(View),median=median(View),st.dev=sd(View),Stocks=length(unique(Stock))),by=.(Method)]),1,'year'))[,Strategy:='CONS']

stat.pt.view <- rbind(pt.rank.views[View!=0,list(mean=mean(View),median=median(View),st.dev=sd(View),Stocks=length(unique(Stock))),by=.(year,Method)],setnames(cbind('Total',pt.rank.views[View!=0,list(mean=mean(View),median=median(View),st.dev=sd(View),Stocks=length(unique(Stock))),by=.(Method)]),1,'year'))[,Strategy:='PT']

stat.eps.view <- rbind(eps.rank.views[View!=0,list(mean=mean(View),median=median(View),st.dev=sd(View),Stocks=length(unique(Stock))),by=.(year,Method)],setnames(cbind('Total',eps.rank.views[View!=0,list(mean=mean(View),median=median(View),st.dev=sd(View),Stocks=length(unique(Stock))),by=.(Method)]),1,'year'))[,Strategy:='EPS']

@@

test <- melt(stat.full,id.vars = c('year','Method','Strategy'))
test.a <- acast(test,year~Method~Strategy~variable,value.var = 'value')

@@

final.bl$Method <- factor(final.bl$Method,levels=strategies)
final.bl$Views <- factor(final.bl$Views,levels=c('CONS','TP','EPS','Market'))
final.bl <- final.bl[,ann.ret:=ann.ret*100][,ann.st:=ann.sd*100]
bl.results <- acast(unique(melt(data = final.bl,id.vars = c('Method','Views'),measure.vars  = c('ann.ret','ann.st','ann.sr','meanViews','Ave.TO')),by=c('Method','variable','Views')),Views~Method~variable,value.var = 'value')

@@

periods <- rbind(final.bl[,data.table(rollapplyr(port.ret,20,roll.ret.f,by=4,partial=F)),by=.(Views,Method)][,strat:='yes'],final.bl[,data.table(rollapplyr(ns.port.ret,20,roll.ret.f,by=4,partial=F)),by=.(Views,Method)][,strat:='no'],final.bl[,data.table(roll.ret.f(port.ret)),by=.(Views,Method)][,strat:='yes'],final.bl[,data.table(roll.ret.f(ns.port.ret)),by=.(Views,Method)][,strat:='no'])[,period:=periods.id,by=.(Views,Method,strat)][,sr:=ann.ret/ann.sd]

periods.array <- acast(melt(periods,id.vars = c('Views','Method','period','strat')),period~Views~Method~strat~variable,value.var = 'value')

>>>>

stat.nr <- rbind(na.omit(nr.views)[,list(mean=mean(View),median=median(View),st.dev=sd(View),Stocks=length(unique(Stock))),by=.(year,Method,type)],setnames(cbind('Total',na.omit(nr.views)[,list(mean=mean(View),median=median(View),st.dev=sd(View),Stocks=length(unique(Stock))),by=.(Method,type)]),1,'year'))[,Strategy:='CONS']

stat.pt.view <- rbind(pt.rank.views[View!=0,list(mean=mean(View),median=median(View),st.dev=sd(View),Stocks=length(unique(Stock))),by=.(year,Method,type)],setnames(cbind('Total',pt.rank.views[View!=0,list(mean=mean(View),median=median(View),st.dev=sd(View),Stocks=length(unique(Stock))),by=.(Method,type)]),1,'year'))[,Strategy:='PT']

stat.eps.view <- rbind(eps.rank.views[View!=0,list(mean=mean(View),median=median(View),st.dev=sd(View),Stocks=length(unique(Stock))),by=.(year,Method,type)],setnames(cbind('Total',eps.rank.views[View!=0,list(mean=mean(View),median=median(View),st.dev=sd(View),Stocks=length(unique(Stock))),by=.(Method,type)]),1,'year'))[,Strategy:='EPS']

@@

test <- melt(stat.full,id.vars = c('year','Method','Strategy','type'))
test.a <- acast(test,year~Method~Strategy~variable~type,value.var = 'value')

@@

final.bl$Method <- factor(final.bl$Method,levels=strategies)
final.bl$Views <- factor(final.bl$Views,levels=c('CONS','TP','EPS','Market'))
final.bl <- final.bl[,ann.ret:=ann.ret*100][,ann.st:=ann.sd*100]
bl.results <- acast(unique(melt(data = final.bl,id.vars = c('Method','Views','type'),measure.vars  = c('ann.ret','ann.st','ann.sr','meanViews','Ave.TO')),by=c('Method','variable','Views','type')),Views~Method~variable~type,value.var = 'value')

@@

periods <- rbind(final.bl[,data.table(rollapplyr(port.ret,20,roll.ret.f,by=4,partial=F)),by=.(Views,Method,type)][,strat:='yes'],final.bl[,data.table(rollapplyr(ns.port.ret,20,roll.ret.f,by=4,partial=F)),by=.(Views,Method,type)][,strat:='no'],final.bl[,data.table(roll.ret.f(port.ret)),by=.(Views,Method,type)][,strat:='yes'],final.bl[,data.table(roll.ret.f(ns.port.ret)),by=.(Views,Method,type)][,strat:='no'])[,period:=periods.id,by=.(Views,Method,strat,type)][,sr:=ann.ret/ann.sd]

periods.array <- acast(melt(periods,id.vars = c('Views','Method','period','strat','type')),period~Views~Method~strat~variable~type,value.var = 'value')
